---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wince

<!-- badges: start -->
<!-- badges: end -->

The goal of wince is to ...


TODO

- [ ] make create_nc and write_nc separate, so create is a function(dimension, extent = NULL, etc)
- [ ] convert to RNetCDF
- [ ] include grid_mapping dummy variable
- [ ] various fixmes, global atts, good names, integer vs float vs byte etc. 


## Installation

You can install the development version of wince like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wince)
## basic example code
f <- write_nc(volcano, extent = c(0, 87, 0, 61), zvar = -1, z_type = "elevation")
tidync::tidync(f)

png <- system.file("textures/world.png", package = "rgl", mustWork = TRUE)
arr <- aperm(png::readPNG(png), c(2, 1, 3))
arr <- arr[,ncol(arr):1, ]
f <- write_nc(arr, extent = c(-180, 180, -90, 90), data_name = "world_image")
terra::plotRGB(terra::rast(f) * 256)
maps::map(add = T)


## in future (we need -expand too though for this palette PNG, or nativeRaster etc)
# imvrt <- vapour::vapour_vrt(png, extent = c(-180, 180, -90, 90), projection = "OGC:CRS84", bands = 1:3)
# arr <- whatarelief::imagery(source = imvrt, extent = ex <- c(-1, 1, -1, 1) * 1e7, projection = "+proj=laea")
# write_nc(arr, extent = ex, projection = "+proj=laea")

```


## Code of Conduct
  
Please note that the wince project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
